Explore resilience evi

### 2018-11-16 analysis/evi/explore_resilience.Rmd
update mhuber export data

```{r wd, echo=FALSE}
#---------------------------------
machine <- 'ajpelu'
#machine <- 'ajpeluLap'
di <- paste('/Users/', machine, '/Dropbox/phd/phd_repos/qpyr_dendro', sep='')
#---------------------------------
```

@@

mhuber_agg <- mhuber %>% 
  mutate(M.Huber = round(M.Huber, 4),
         lower.ci = round(lower.ci, 4),
         upper.ci = round(upper.ci, 4)) %>% 
  unite_("ci", c("lower.ci", "upper.ci"), sep=",") %>% 
  mutate(ci = paste0('(', ci, ')')) %>% 
  dplyr::select(-MonoLetter) %>% 
  dplyr::select(var, disturb_year:ci, Letter) %>% as.data.frame()

@@

mhuber_agg_a <- mhuber_a %>% 
  mutate(M.Huber = round(M.Huber, 4),
         lower.ci = round(lower.ci, 4),
         upper.ci = round(upper.ci, 4)) %>% 
  unite_("ci", c("lower.ci", "upper.ci"), sep=",") %>% 
  mutate(ci = paste0('(', ci, ')')) %>% 
  dplyr::select(-MonoLetter) %>% 
  dplyr::select(var, disturb_year:ci, Letter) %>% as.data.frame()

@@

mhuber_agg_b <- mhuber_b %>% 
  mutate(M.Huber = round(M.Huber, 4),
         lower.ci = round(lower.ci, 4),
         upper.ci = round(upper.ci, 4)) %>% 
  unite_("ci", c("lower.ci", "upper.ci"), sep=",") %>% 
  mutate(ci = paste0('(', ci, ')')) %>% 
  dplyr::select(-MonoLetter) %>% 
  dplyr::select(var, site:ci, Letter) %>% as.data.frame()

>>>>

# ```{r wd, echo=FALSE}
# #---------------------------------
# machine <- 'ajpelu'
# #machine <- 'ajpeluLap'
# di <- paste('/Users/', machine, '/Dropbox/phd/phd_repos/qpyr_dendro', sep='')
# #---------------------------------
# ```

@@

mhuber_agg <- mhuber %>% 
  mutate_at(.vars = c("M.Huber", "lower.ci", "upper.ci"), funs(round(., 4))) %>% 
  dplyr::select(var, disturb_year:Letter) %>% as.data.frame()

@@

mhuber_agg_a <- mhuber_a %>% 
  mutate_at(.vars = c("M.Huber", "lower.ci", "upper.ci"), funs(round(., 4))) %>% 
  dplyr::select(var, disturb_year:Letter) %>% as.data.frame()

@@

mhuber_agg_b <- mhuber_b %>% 
  mutate_at(.vars = c("M.Huber", "lower.ci", "upper.ci"), funs(round(., 4))) %>% 
  dplyr::select(var, site:Letter) %>% as.data.frame()
